Paper_Cartama_Microbial_ecology

### 2022-03-07 R/Paper_plots_microbial_ecology.Rmd
dru

library(tidyverse)
library(gridExtra)
library(tibble)
library(ggplot2)
library(extrafont)
loadfonts(device = "win")
library(phyloseq)
library(scales)   
library(ggpubr)
library(readxl)
library(vegan)
library(biomformat)

@@

```{r alfa df}
Alfa <- read_excel("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/Alfa/Alfa.xlsx")
head(Alfa)
```
Ploting the alpha_diversity metrics

@@

```{r uploading the CCS.biom and tree.nwk}
biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/css_eff.biom")
biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
sam <-sample_data(biomfile_merged)

@@

tree <- read_tree("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/tree.nwk")

@@

```{r data barplot}
biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/ASVs_table9_dada2R.biom")
biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
#sample_data(biomfile_merged)

@@

library(patchwork)
p2/p3 
```

>>>>

library(tidyverse)
library(gridExtra)
library(tibble)
library(ggplot2)
library(extrafont)
loadfonts(device = "win")
library(phyloseq)
library(scales)   
library(ggpubr)
library(readxl)
library(vegan)
library(biomformat)
library(patchwork)

path<-"C:/Users/Dru/Desktop/Cartama_paper/files/MicrobialEcology"

@@

```{r alfa df}
Alfa <- read_excel(paste(path,"/Alfa.xlsx",sep=""))
head(Alfa)
```
Ploting the alpha_diversity metrics

@@

```{r uploading the CCS.biom and tree.nwk}
biomfile <- import_biom(paste(path,"/css_eff.biom",sep=""))
biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
sam <-sample_data(biomfile_merged)

@@

tree <- read_tree(paste(path,"/tree.nwk",sep=""))

@@

```{r data barplot}
biomfile <- import_biom(paste(path,"/ASVs_table9_dada2R.biom",sep=""))
biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
#sample_data(biomfile_merged)

@@

p2/p3 
```
